---
title: "Victoria, BC, Canada: climate norms"
output: html_notebook
---

This file creates a single csv file with 1981-2010 climate norms sourced from Environment Canada.

* source page: https://climate.weather.gc.ca/climate_normals/index_e.html

The html tables were copied to the clipboard and pasted as tribble text using the [{datapasta}](https://milesmcbain.github.io/datapasta/) package Addins to RStudio

```{r setup}
# tidyverse
library(dplyr)
library(tidyr)

# utilities
library(here)

```

The weather station is VICTORIA INT'L A (the Victoria International Airport)

Latitude:48°38'50.010" N
Longitude:123°25'33.000" W
Elevation:19.50 m
Climate ID:1018620
WMO ID:71799
TC ID:YYJ


https://climate.weather.gc.ca/climate_normals/results_1981_2010_e.html?searchType=stnName&txtStationName=victoria&searchMethod=contains&txtCentralLatMin=0&txtCentralLatSec=0&txtCentralLongMin=0&txtCentralLongSec=0&stnID=118&dispBack=0




```{r}
df_1018620 <- 
read_csv(here("data", "normals-1018620-1981-2010.csv"),
         skip = 14)

df_vicint <- df_1018620 %>% 
  rename("measure" = X1) %>% 
  select(measure:Dec)

df_vicint  

```


Structure as Japanese table:

+----------+------+
| Japan    | Canada  |
+==========+======+
| daily_mean_temp_C  | "Daily Average (°C)" |
+----------+------+
| daily_max_temp_C  | "Daily Maximum (°C)" |
+----------+------+
| daily_min_temp_C  | "Daily Minimum (°C)" |
+----------+------+
| precipitation_mm  | "Precipitation (mm)" |
+----------+------+
| relative_humidity_pct | "Average Relative Humidity - 1500LST (%)" |
+----------+------+
| sunshine_duration_hrs  | "Total Hours" |
+----------+------+

```{r}

measure_list <- c(
  "daily_mean_temp_C",
  "daily_max_temp_C",
  "daily_min_temp_C",
  "precipitation_mm",
  "relative_humidity_pct",
  "sunshine_duration_hrs"
)

df_vicint_climate <-
df_vicint %>% 
  pivot_longer(-measure, names_to = "month", values_to = "value") %>% 
  mutate("Station" = "Victoria") %>%
  mutate(measure2 = case_when(
    measure == "Daily Average (°C)" ~ "daily_mean_temp_C",
    measure == "Daily Maximum (°C)" ~ "daily_max_temp_C",
    measure == "Daily Minimum (°C)" ~ "daily_min_temp_C",
    measure == "Precipitation (mm)" ~ "precipitation_mm",
    measure == "Average Relative Humidity - 1500LST (%)" ~ "relative_humidity_pct",
    measure == "Total Hours" ~ "sunshine_duration_hrs",
    TRUE ~ measure)
    ) %>% 
  filter(measure2 %in% measure_list) %>% 
  select(Station, month, measure2, value) %>% 
  rename("measure" = measure2) %>% 
  pivot_wider(Station:month, names_from = measure, values_from = value) %>% 
  select(-sunshine_duration_hrs, sunshine_duration_hrs)

df_vicint_climate

df_vicint_climate <- df_vicint_climate %>% 
  mutate_at(measure_list, as.numeric)

write_csv(df_vicint_climate, here("data", "vicint_climate.csv"))
saveRDS(df_vicint_climate, file = here("data", "vicint_climate.rds"))

```



